Museum collections as baseline for assessing the global pollinator crisis

### 2018-06-12 ms.Rmd
new commit

#read in data
declines <- read.csv(file = "data/richness_declines.V2.csv", header = TRUE, sep = ",", na.strings=c("","NA"))
#nothing outside EU- USA. Spain and NZ can be added.

>>>>

#read in data
declines <- read.csv(file = "data/richness_declines.V2.csv", header = TRUE, sep = ",", na.strings=c("","NA"),fileEncoding="latin1")
#nothing outside EU- USA. Spain and NZ can be added.
